Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-22 paper.tex
Sistemata didascalia

%What are the key components of my approach and results? Also include any specific limitations.
We address the detection of camera blurring and displacement (Section \ref{sec:probForm}), and propose an algorithm (Section~\ref{sec:propSol}) that relies on indicators that can be easily computed in low-power smart cameras. We monitor the average image intensity or frame difference (to detect camera displacement), and the average gradient norm (to detect blurring), and consider any frame yielding an outlier as tampered. In particular, we show that separately monitoring these indicators over different regions of the image can substantially improve the displacement-detection performance. Image regions are defined during an initial configuration phase (Section \ref{subsec:Segmentation}), thus the algorithm operates at a negligible computational overhead w.r.t. monitoring the whole image (Section \ref{subsec:coputationalComplexity}). Our algorithm thus represents a prompt trigger, to be possibly combined with other sequential monitoring techniques. Experiments (Section \ref{sec:experiments}) show that leveraging image regions can substantially improve the displacement-detection performance. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

@@

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values between $0.1$ and $50$, with step $0.1$. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY$_\gamma$, RECALL$_\gamma$) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption indicate that camera displacements can be effectively detected by all the considered methods; the comparison against Voronoi regions suggests that a more substantial advantage is guaranteed when regions fit the scene content. As far as the values of $\Gamma_l$ and $\Gamma_d $ are concerned, the best option is to raise an alert as soon as a single region provides a very clear outlier (i.e., interval \eqref{eq:confidenceRegions} are quite wide). This option is preferable with respect to requiring $K-1$ regions to simultaneously fire an outlier, because it also enable the detection of partial occlusions of the scene. Overall, the ROC curves confirm that $d$ is a far more effective indicator than $l$ in detecting camera displacements.\\
Considering $d$ as indicator, we observe that to limit FPs to $1\%$, Algorithm~\ref{alg:DISPL} have a recall of $99.92\%$, with $\gamma = 15.6$, while considering the whole image solution decreases TPs to $91.67\%$ ($\gamma = 6.5$), as for considering Voronoi's regions ($89.05\%$, $\gamma = 18.64$).
Considering $l$ as indicator, instead, limit FPs to $1\%$ brings a recall of $73.98\%$ when using Algorithm~\ref{alg:DISPL} ($\gamma=5.8$), more than considering the whole image solution ($17.85\%$, $\gamma=3.7$), and Voronoi's regions ($53.02\%$, $\gamma=6$).
Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.\\ %\gi{Aggiornare con i nuovi dati}
%\emph{Considering $d$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.4\%$ of false alarms, with $\gamma = 24.7$, which is less than one fifth of the whole image solution ($2.2\%$ with $\gamma = 4.6$) and the Voronoi solution ($2.3\%$ with $\gamma = 12.9$).
%On the other side, considering $l$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $13\%$ of false alarms, with $\gamma = 2.5$, which is about one sixth of the whole image solution ($75\%$ with $\gamma = 0.1$) and about three fifty than the Voronoi solution ($22\%$ with $\gamma = 1.7 $).
%Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
In contrast, Figure~\ref{fig:ROC}(c) confirms that blurring \ad{Giacomo: blurs?} are more effectively detected by monitoring the whole scene at once. This is probably due to the fact that typically, regions $\{R_k\}$ do not include the most prominent edge of the scene, which are indeed the most informative part to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.%\gi{aggiungere commento su K-1 vornoi che va meglio?}

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curve for displacement detection considering Frame Difference (FD) as indicator.
	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ Region - Algorithm $1$) is $99.89\%$, while the AUC of considering the whole image (Total) is $99.65\%$. 
	%the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
	\textbf{(b)} ROC curve for displacement detection considering Luma as indicator.
	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ Region - Algorithm $1$) is $98.44\%$, while the AUC of considering the whole image (Total) is $84.07\%$. 
	\textbf{(c)} ROC curve for blurring detection.
	In this case, the Gradient-Total (AUC $99.13\%$) outperforms the Gradient-Regions (AUC $98.4\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image. 
	For the visualization sake, ROC curves \textbf{(a)} and \textbf{(c)} have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms.
	}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}

>>>>

%What are the key components of my approach and results? Also include any specific limitations.
We address the detection of camera blurring and displacement (Section \ref{sec:probForm}), and propose an algorithm (Section~\ref{sec:propSol}) that relies on indicators that can be easily computed in low-power smart cameras. We monitor the average image intensity or frame difference (FD) (to detect camera displacement), and the average gradient norm (to detect blurring), and consider any frame yielding an outlier as tampered. In particular, we show that separately monitoring these indicators over different regions of the image can substantially improve the displacement-detection performance. Image regions are defined during an initial configuration phase (Section \ref{subsec:Segmentation}), thus the algorithm operates at a negligible computational overhead w.r.t. monitoring the whole image (Section \ref{subsec:coputationalComplexity}). Our algorithm thus represents a prompt trigger, to be possibly combined with other sequential monitoring techniques. Experiments (Section \ref{sec:experiments}) show that leveraging image regions can substantially improve the displacement-detection performance. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

@@

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values between $0.1$ and $50$, with step $0.1$. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY$_\gamma$, RECALL$_\gamma$) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption indicate that camera displacements can be effectively detected by all the considered methods; the comparison against Voronoi regions suggests that a more substantial advantage is guaranteed when regions fit the scene content. As far as the values of $\Gamma_l$ and $\Gamma_d $ are concerned, the best option is to raise an alert as soon as a single region provides a very clear outlier (i.e., interval \eqref{eq:confidenceRegions} are quite wide). This option is preferable with respect to requiring $K-1$ regions to simultaneously fire an outlier, because it also enable the detection of partial occlusions of the scene. Overall, the ROC curves confirm that $d$ is a far more effective indicator than $l$ in detecting camera displacements.\\
Considering $d$ as indicator, we observe that to limit FPs to $1\%$, Algorithm~\ref{alg:DISPL} have a recall of $99.92\%$, with $\gamma = 15.6$, while considering the whole image solution decreases TPs to $91.67\%$ ($\gamma = 6.5$), as for considering Voronoi's regions ($89.05\%$, $\gamma = 18.64$).
Considering $l$ as indicator, instead, limit FPs to $1\%$ brings a recall of $73.98\%$ when using Algorithm~\ref{alg:DISPL} ($\gamma=5.8$), more than considering the whole image solution ($17.85\%$, $\gamma=3.7$), and Voronoi's regions ($53.02\%$, $\gamma=6$).
Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.\\ %\gi{Aggiornare con i nuovi dati}
%\emph{Considering $d$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.4\%$ of false alarms, with $\gamma = 24.7$, which is less than one fifth of the whole image solution ($2.2\%$ with $\gamma = 4.6$) and the Voronoi solution ($2.3\%$ with $\gamma = 12.9$).
%On the other side, considering $l$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $13\%$ of false alarms, with $\gamma = 2.5$, which is about one sixth of the whole image solution ($75\%$ with $\gamma = 0.1$) and about three fifty than the Voronoi solution ($22\%$ with $\gamma = 1.7 $).
%Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
In contrast, Figure~\ref{fig:ROC}(c) confirms that blurring is more effectively detected by monitoring the whole scene at once. This is probably due to the fact that typically, regions $\{R_k\}$ do not include the most prominent edge of the scene, which are indeed the most informative part to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.%\gi{aggiungere commento su K-1 vornoi che va meglio?}

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curves relative to displacement detection based on FD: the AUC obtained by 
"Algo 1 on one region" is $99.89\%$, while the AUC obtained by "Total" (on the whole 
image) is $99.65\%$.
\textbf{(b)} ROC curves relative to displacement detection based on Luma: the AUC obtained by 
"Algo 1 on one region" is $98.44\%$, while the AUC obtained by "Total" (on the whole 
image) is $84.07\%$.
\textbf{(c)} ROC curves relative to blurring detection based on Gradient: as opposed to \textbf{(a)} and 
\textbf{(b)}, "Algo 1 on one region" (AUC $98.4\%$) is outperformed by "Total" (AUC $99.13\%$).
Note that, in order to highlight the details, the ROC curves are drawn with different 
scales.}
%\caption{\textbf{(a)} ROC curve for displacement detection considering Frame Difference (FD) as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $99.89\%$, while the AUC of considering the whole image (Total) is $99.65\%$. 
%	%the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
%	\textbf{(b)} ROC curve for displacement detection considering Luma as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $98.44\%$, while the AUC of considering the whole image (Total) is $84.07\%$. 
%	\textbf{(c)} ROC curve for blurring detection.
%	In this case, the Gradient-Total (AUC $99.13\%$) outperforms the Gradient-Regions (AUC $98.4\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. %This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image. 
%	ROC curves \textbf{(a)} and \textbf{(c)}
%	%For the visualization sake, ROC curves \textbf{(a)} and \textbf{(c)} have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms.
	%}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}
